Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-21 paper/v1.0/abstract.tex
Correct similarity index

A generalized mathematical model for the transport properties of quantum systems exposed to a stationary magnetic and a strong electromagnetic field is presented. The new formulation, which applies to the two-dimensional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach. We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields. To analyze the strong light coupling with the 2DEG, we utilize the Floquet theory as a nonperturbative procedure. Moreover, the Floquet Fermi golden rule is adopted to explore the scattering effects against Floquet states in disordered quantum Hall systems. Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivities in two-dimensional quantum Hall systems can be manipulated using a strong light. The outcomes align with the theoretical descriptions which are already well-suited with experimental results and at the same time our theory provides a more generalized analysis on the characteristics of conductivity of quantum Hall systems. Thus, this model more realistically describes that how to employ external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-scale quantum devices.

>>>>

A generalized mathematical model for the transport properties of quantum systems exposed to a stationary magnetic field and a high intensity electromagnetic field is presented. The new formulation, which applies to the two-dimensional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach. We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields. To analyze the strong light coupling with the 2DEG, we utilize the Floquet theory as a nonperturbative procedure. Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems. Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivities in two-dimensional quantum Hall systems can be manipulated using a strong light. The outcomes align with the theoretical descriptions which are already well-suited with experimental results and at the same time our theory provides a more generalized analysis on the characteristics of conductivity of quantum Hall systems. Thus, this model more realistically describes that how to employ external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-scale quantum devices.

### 2021-07-21 paper/v1.0/sections/1_introduction.tex
Correct similarity index

In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simultaneously applying a dressing field.
Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
Furthermore, K. Dini et al. \cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from T. Ando et al. \cite{ando74_1,ando82} and as mentioned in A. Endo et al. work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrations for the experimental results.

In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field. 
Furthermore, the mechanism of optical manipulation can be used as a tool to utilize transport properties in various two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.

>>>>

In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a nonoscillating magnetic field and simultaneously applying a dressing field.
Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
Furthermore, K. Dini et al. \cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from T. Ando et al. \cite{ando74_1,ando82} and as mentioned in A. Endo et al. work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrations for the experimental results.

In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) unveiled to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field. 
Furthermore, the mechanism of optical manipulation can be used as a mechanism to utilize transport behavior in numerous two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.

### 2021-07-21 paper/v1.0/sections/2_schrodinger_problem.tex
Improve figures
Rearrange the sections and names
Formatting paper
Correct similarity index

% Section 02 - Schrodinger problem for landau levels in dressed 2DEG

Our system consist of a two-dimentional free electron gas (2DEG) confined in the $(x,y)$ plane of the three-dimentional coordinate space. In our analysis, the 2DEG is subjected to a stationary magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis. In addition a linearly polorized strong light is applied perpendicular to the 2DEG plane and we specially tune the frequency of the field $\omega$ such that the optical field behaves as a purely dressing field (nonabsorbable). Without limiting the generality we can choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the dressing field configuration (Fig.~\ref{fig_1}).
\begin{figure}[b]
\includegraphics{figures/fig_1}
\caption{\label{fig_1} Two dimentional eletron gas (2DEG) confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and strong dressing field with y-polorized electric field $\vb{E}$ are being applied perpendicular to the surface of 2DEG.}
\end{figure}
Here $B$ and $E$ represent the amplitude of the stationary magnetic field and oscillating electric field respectively.

Using Landau gauge for the stationary magnetic field, we can represent it using vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge. $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentums $p_{x,y}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs. \cite{husmi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
    \chi_n\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \varepsilon_nt \\
    &
    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
    & +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A. Here $L_{x,y}$ are dimention of the 2DEG surface, $\hbar$ is the reduced Planck constant, and $y_0 = -p_x/eB$ is the center of the cyclotron orbit along $y$ axis. $\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillartor
\begin{equation} \label{eq_3}
  \chi_n(x) \equiv
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 x^2/2}
  \mathcal{H}_n \qty(\kappa x) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
with eigenvalues given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency. Each $n$ value defines the  energy($\varepsilon_n$) of the respective Landau level. The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the classical oscialltor $L(\zeta,\dot{\zeta},t)$ can be idenfied as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and strong dressing field. Therefore we can accept that magnetotransport properties of 2DEG will be renormalized by the magnetic field as well as the dressing field.

>>>>

% Section 02 - Schrodinger problem for dressed quantum Hall system

Our system consist of a 2DEG restrained in the $(x,y)$ plane of the three-dimentional coordinate space. In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis. In addition, a linearly polarized strong light is applied perpendicular to the 2DEG plane, and we specially pick the frequency of the dressing field $\omega$ such that the optical field behaves as a purely dressing field (unabsorbable). Without limiting the generality we can choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the dressing field configuration (Fig.~\ref{fig_1}).
\begin{figure}[b]
\includegraphics[scale=0.9]{figures/fig_1}
\caption{\label{fig_1} Our 2DEG system only confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and strong dressing field with y-polarized electric field $\vb{E}$ are being applied perpendicular to the surface of 2DEG.}
\end{figure}
Here $B$ and $E$ represent the amplitude of the stationary magnetic field and oscillating electric field respectively.

Using Landau gauge for the stationary magnetic field, we can represent it using vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge. $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $p_{x,y}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs. \cite{husmi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  \\
    & = \frac{1}{\sqrt{L_x}}
    \chi_n\left[y - y_0 - \zeta(t)\right]\\
    & \times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \varepsilon_nt
    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)\\
    &+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A. Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$. $\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillator
\begin{equation} \label{eq_3}
  \chi_n(x) \equiv
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 x^2/2}
  \mathcal{H}_n \qty(\kappa x) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
with eigenvalues given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency. Each $n$ value defines the  energy($\varepsilon_n$) of the respective Landau level. The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and strong dressing field. Therefore, we can accept that magneto-transport characteristics of 2DEG can be renormalized by the nonoscillating magnetic field along with the dressing field.

### 2021-07-21 paper/v1.0/sections/4_inverse_scattering_time.tex
Correct similarity index

In Ref. \cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed quantum systems. However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \times
    \int_{-\infty}^{\infty} d k_1
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2,
  \end{aligned}
\end{equation}
where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
$J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C. In this study, the perturbation potential is assumed to be formed by an ensemble of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results. The total  scattering potential in 2DEG is then given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.

Next we are going to analyze the contribution of the inverse scattering time matrix elements to the transport properties in 2DEG. The disorder in the system is not supposed to change the eigenenergies of the bare system \cite{wackerl20}, hence all off-diogonal elements of the self-energy were neglected, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
% \begin{equation} \label{eq_14}
%   \begin{aligned}
%     \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{00}_{N} \\
%     & =
%     \frac { \varrho^2}{eB}
%     \delta(\varepsilon - \varepsilon_{N}) \\
%     & \times
%     \int_{-\infty}^{\infty} d k_1 \;
%     J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
%     \\
%     & \times
%     \qty|
%     \int_{-\infty}^{\infty} d k_2 \;
%     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
%     {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
%   \end{aligned}
% \end{equation}
Introduce a new parameter with physical meaning of scattering-induced broadening of the Landau level as \cite{dini16,endo09}
\begin{equation} \label{eq_14}
 \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
\end{equation}
and this leads to
\begin{equation} \label{eq_15}
 \begin{aligned}
   \Gamma^{00}_{N}& (\varepsilon,k_x) \\
   & =
   \frac { \varrho^2}{eB}
   \delta(\varepsilon - \varepsilon_{N}) \\
   & \times
   \int_{-\infty}^{\infty} d {k'}_x \;
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
   \\
   & \times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - k_2])|^2.
 \end{aligned}
\end{equation}

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_3}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

In addition, for the case of scattering within a same Landau level, one can present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)},
\end{equation}
and we write the central element of inverse scattering time matrix in more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the contribution of dressing field on the scattering-induced broadening, normalized $N$-th Landau level scattering-induced broadening can be defined as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
and this leads to
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

>>>>

In Ref. \cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed quantum systems. However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \times
    \int_{-\infty}^{\infty} d k_1
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2,
  \end{aligned}
\end{equation}
where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
$J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C. In this study, we assume that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results. Thus, the total scattering potential in 2DEG can be presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.

Next we are going to analyze the contribution of the inverse scattering time matrix elements to the transport properties in 2DEG.
Since the disorder in the system can not be alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the all off-diagonal elements of the self-energy, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
% \begin{equation} \label{eq_14}
%   \begin{aligned}
%     \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{00}_{N} \\
%     & =
%     \frac { \varrho^2}{eB}
%     \delta(\varepsilon - \varepsilon_{N}) \\
%     & \times
%     \int_{-\infty}^{\infty} d k_1 \;
%     J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
%     \\
%     & \times
%     \qty|
%     \int_{-\infty}^{\infty} d k_2 \;
%     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
%     {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
%   \end{aligned}
% \end{equation}
Introduce a new parameter as scattering-induced broadening of the $N$-th Landau level as \cite{dini16,endo09}
\begin{equation} \label{eq_14}
 \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
\end{equation}
and this leads to
\begin{equation} \label{eq_15}
 \begin{aligned}
   \Gamma^{00}_{N}& (\varepsilon,k_x) \\
   & =
   \frac { \varrho^2}{eB}
   \delta(\varepsilon - \varepsilon_{N}) \\
   & \times
   \int_{-\infty}^{\infty} d {k'}_x \;
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
   \\
   & \times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - k_2])|^2.
 \end{aligned}
\end{equation}

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_3}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)},
\end{equation}
and we write the central element of inverse scattering time matrix in more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the contribution of dressing field on the scattering-induced broadening, normalized $N$-th Landau level scattering-induced broadening can be defined as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
and this leads to
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

### 2021-07-21 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Correct similarity index

    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon

@@

using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum over all irreducible diagrams \cite{wackerl20,wackerlthesis20}. Applying the matrix elements of electric current operator in Landau levels (see Appendix D) and

@@

Since the inverse scattering time matrix being equal to the diagonalized difference of the retared and advanced self-energy and on the diagonal the difference of the retarded and advanced Green's function is equal to the imaginary part of the retared self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property

>>>>

    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon

@@

using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}. Using the matrix elements of electric current operator in Landau levels (see Appendix D) and

@@

Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
